Appendix

### 2024-09-05 manuscript/manuscript_appendix.Rmd
Preparation for comparing type I error rates.

# Appendix D: Experimental results using location- and scale-invariant Box-Cox transformation

>>>>

# Appendix D: Empirical central normality test

The empirical central normality test was derived using data sampled from asymmetric generalised normal distributions, including outliers, to resemble more realistic datasets.
Here we assess the type I error rate of two, less realistic, sets of data:

1. Data sampled from asymmetric generalised normal distributions without outliers.
2. Data sampled from normal distributions without outliers, without any power transformation applied.

Other aspects of the experiment remain the same.
Thus, we first drew $m_d=10000$ random distributions.
For asymmetric generalised normal distributions, each distribution was parametrised with a randomly chosen skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$.
For fully normal distributions, skewness parameter $\alpha = 0.5$ and shape parameter $\beta = 2.0$ were fixed.
Location and scale parameters were set as $\mu = 0$ and $\sigma = 1$, respectively.
$n = \lceil 10^\gamma \rceil$ values were then randomly drawn, with $\gamma \sim U\left(1.47, 3.00\right)$, which led to between $30$ and $1000$ values being drawn to create $\mathbf{X}_i$.
Residuals were then computed after performing robust location- and scale-invariant transformations with the empirical tapered cosine weighting method for the dataset with asymmetric generalised normal distributions,
and without any transformation for the dataset with only normal distributions.

```{r empirical-central-normality-test-appendix, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Blabla"
)

# Appendix E: Experimental results using location- and scale-invariant Box-Cox transformation
